---
title: "Prediction of a diamond price"
author: "Daria Stepanyan"
date: "June 26, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning = FALSE, cache = TRUE)
```

## Purpose of the app
This app is intended for demonstration of 'shiny' features for ['Developing Data Products'](https://www.coursera.org/learn/data-products/home/welcome) course on Coursera.

The app is going to predict a price of a diamond based on its parameters using a linear model and display it on a plot.

## Data

Presented shiny app uses the 'diamonds' dataset from ggplot2 package in R. It contains the prices and other attributes of almost 54,000 diamonds.

```{r data}
str(diamonds)
```

## Model

For prediction the following model was chosen. It's simple yet explains rather most of the variance

```{r model}
fit <- lm(price ~ carat + cut + color + clarity, data = diamonds)
summary(fit)$r.squared
```

## Interface

You can find the app here: 



## Slide with Plot

```{r pressure}
plot(pressure)
```

